logistic regression

### 2021-07-01 scripts/57_16s_lefse.Rmd
update

# the asv to keep
# keep the asvs that show up in at least 10% of the samples
keepg <- cts_all %>% 
  filter(relab > 0.0001) %>%
  ungroup() %>% 
  count(taxa_asv) %>% 
  filter(n > floor(nrow(meta) * 0.1)) %>% 
  pull(taxa_asv)

@@

```{r}
# dat <- genera %>% 
#   filter(genus == 'Ruminococcus') %>% 
#   gather('sampleid', 'relab', names(.)[2]:names(.)[ncol(.)]) %>% 
#   full_join(meta) %>% 
#   mutate(logrelab =  log10(relab + 2e-6)) 
# 
# yes <- dat %>% 
#   filter(cr_d100 == 'yes')
# no <- dat %>% 
#   filter(cr_d100 == 'no')
# 
# 
# dat %>% 
#   #filter(center == 'M') %>% 
#   mutate(logrelab =  log10(relab + 2e-6)) %>% 
#   ggboxplot(x = 'cr_d100', y = 'logrelab', add = 'jitter') +
# stat_compare_means(comparisons= list(c('yes', 'no')),
# 										label= "p.signif",
# 										method= 'wilcox.test',
# 										correct=FALSE)
# 
# t.test(yes$logrelab, no$logrelab)

>>>>

# the asv to keep
# keep the asvs that show up in at least 25% of the samples
keepg <- cts_all %>% 
  filter(relab > 0.0001) %>%
  ungroup() %>% 
  count(taxa_asv) %>% 
  filter(n > floor(nrow(meta) * 0.25)) %>% 
  pull(taxa_asv)

@@

### 2021-07-01 scripts/62_logistic_regression_version.Rmd
update

```{r}
library(magrittr)
library(ggeffects)
library(tidyverse)
library(lme4)
```

@@

@@

ggpredict(m_tox,se=TRUE,interactive=TRUE,digits=3, c('simpson_reciprocal','center')) %>% plot()
```

@@

ggpredict(m_CR,se=TRUE,interactive=TRUE,digits=3, c('simpson_reciprocal','center')) %>% plot()
```

@@

@@

gmeta <- meta  %>% 
  inner_join(genera) %>% 
  select(toxicity,cr_d100, Akkermansia,Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus , center)
```

@@

ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides','center')) %>% plot()
ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus','center')) %>% plot()
ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus','center')) %>% plot()
ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia','center')) %>% plot()
ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium','center')) %>% plot()
```

@@

ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides','center')) %>% plot()
ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus','center')) %>% plot()
ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus','center')) %>% plot()
ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia','center')) %>% plot()
ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium','center')) %>% plot()
```

>>>>

```{r}
library(magrittr)
library(ggeffects)
library(tidyverse)
library(lme4)
library(cowplot)
library(grid)
library(ggpubr)
```

@@

**The ggeffects package computes estimated marginal means (predicted values) for the response, at the margin of specific values or levels from certain model terms, i.e. it generates predictions by a model by holding the non-focal variables constant and varying the focal variable(s). ggpredict() uses predict() for generating predictions**

@@

ggpredict(m_tox,se=TRUE,interactive=TRUE,digits=3, c('simpson_reciprocal')) %>% plot()
```

@@

ggpredict(m_CR,se=TRUE,interactive=TRUE,digits=3, c('simpson_reciprocal')) %>% plot()
```

@@

The genera's relative abundance is log10 transformed.

@@

# the CLR transformed genera abundance 
clr <- read_csv('../data/amplicon/stool/counts_genus_combined_CLR.csv')  %>% 
  spread(key = 'genus', value = 'clr')

gmeta <- meta  %>% 
  inner_join(clr) %>% 
  select(toxicity,cr_d100, Akkermansia,Bacteroides, Enterococcus, Faecalibacterium, Ruminococcus , center)

gmeta %>% 
  head
```

@@

gb <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides')) %>% plot()
gr <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus')) %>% plot()
ge <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus')) %>% plot()
ga <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia')) %>% plot()
gf <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium')) %>% plot()

gtox <- ggarrange(gb, gr, ge, ga, gf,
    ncol = 1
    #o = 'hv',
    #labels = 'AUTO',
    #axis = 'bltr'
    ) +
    ggsave(str_glue('../figs/amplicon/gtox_CLR_5.pdf'), width = 3, height = 8, dpi = 300)
```

@@

gb <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides')) %>% plot()
gr <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus')) %>% plot()
ge <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus')) %>% plot()
ga <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia')) %>% plot()
gf <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium')) %>% plot()

gCR <- ggarrange(gb, gr, ge, ga, gf,
    ncol = 1
    #o = 'hv',
    #labels = 'AUTO',
    #axis = 'bltr'
    ) +
    ggsave(str_glue('../figs/amplicon/gcr_CLR_5.pdf'), width = 3, height = 8, dpi = 300)
```
